Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-03-29 paper/AlignedIsotropicGW.tex
fixed issue with sigma plot

%
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{../plots/sigma_v_alpha.png}
\caption{\textbf{Effect of small spins on evidence ratio of aligned against isotropic models} The blue line shows the evidence ratio (plotted as the equivalent sigma) between a model where all systems are aligned, versus one where all systems are from an isotropic distribution as a function of the power law $\alpha$ corresponding to Equation~\ref{eq:lowspinalpha}.  The top axis shows the mean spin magnitude $a$
that the value of alpha corresponds to. We see that for mean spin magnitudes $\lesssim 0.2$ we find no evidence for either distribution over the other.}
\label{fig:smallspinsalpha}
\end{figure}
%

>>>>

%
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{../plots/sigma_v_alpha.png}
\caption{\textbf{Effect of small spins on evidence ratio of aligned against isotropic models} The blue line shows the evidence ratio (plotted as the equivalent sigma $\sigma_\mathrm{A/I}$) between a model where all systems are aligned, versus one where all systems are from an isotropic distribution as a function of the power law $\alpha$ corresponding to Equation~\ref{eq:lowspinalpha}.  The top axis shows the mean spin magnitude $\bar{a}$
that the value of $\alpha$ corresponds to. $\alpha = 0$ corresponds to the ``flat'' spin magnitude model, $\alpha = 1$ corresponds to the ``low'' model. We see that for mean spin magnitudes $\lesssim 0.2$ we find no evidence for either distribution over the other.}
\label{fig:smallspinsalpha}
\end{figure}
%
